---
title: "10a_WeightDiss_Analysen"
author: "Johanna Bogon, Julian Högerl, Martin Kocur, Niels Henze, & Martin Riemer"
date: "`r Sys.Date()`"
format: 
  html: 
    toc: true
    embed-resources: true
---

# Preprocessing

## Setup

```{r message=FALSE}

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

rm(list = setdiff(ls(),"data_raw"))
library(tidyverse)
library(knitr)

```

## Read raw data

```{r message=FALSE}
# manually deleted first row in "2022-03-08_10-54-19_log_file.csv" (duplicated header)

# read data

 data_raw <- list.files("../data", pattern = ".txt", full.names = TRUE) %>%
  map(read_delim) %>%
  bind_rows()

head(data_raw)
```

## define factors

```{r}
data_pp <- data_raw


# factors
data_pp <- data_pp %>%
  mutate(
    id = factor(id),
    real_weight = factor(real_weight),
    virtual_weight = factor(virtual_weight)
  )
```


## Remove invalid data

```{r}
  # remove participant 16's data, due to methological error (unaccounted colour blindness)
n <- nrow(data_pp)

data_pp <- filter(data_pp, id != 16 )

cat("Deleted: ", n - nrow(data_pp), " trials")

```

```{r}
# delete practice trials 
n <- nrow(data_pp)

data_pp <- filter(data_pp, block > 0)

cat("Deleted: ", n - nrow(data_pp), " trials")
```

## check trials per subject

```{r}
# counting relevant trials per subject (=> 280)
# for calculating rate of included trials at End of RT-Preprocessing
data_pp <- data_pp %>%
  group_by(id) %>%
  mutate(n_trials = n()) %>%
  ungroup()

range(data_pp$n_trials)
```

## reduce noise

```{r}
# inspect movement time data
ggplot(data_pp,aes(id, rt_ms)) +
  geom_boxplot()
```

```{r}
# inspect tracked path data
ggplot(data_pp,aes(id, tracked_path)) +
  geom_boxplot()
```

```{r}
# delete extreme rts (3000 ms too strict?) and extreme tracked path (6m)
n <- nrow(data_pp)

data_pp <- filter(data_pp, rt_ms < 3000)
data_pp <- filter(data_pp, tracked_path < 6)

cat("Deleted: ", n - nrow(data_pp), " trials")
```

```{r}
# identify all path and rt-Values > 3SDs
data_pp <- data_pp %>%
  group_by(id, real_weight, virtual_weight) %>%
  mutate(
    rt_ms_mean = mean(rt_ms),
    rt_ms_sd = sd(rt_ms),
    rt_ms_z = ((rt_ms - rt_ms_mean) / rt_ms_sd),
    tracked_path_mean = mean(rt_ms),
    tracked_path_sd = sd(rt_ms),
    tracked_path_z = ((rt_ms - rt_ms_mean) / rt_ms_sd)
  ) %>%
  ungroup()

filter(data_pp, rt_ms_z <= -3 | rt_ms_z >= 3 | tracked_path_z <= -3 | tracked_path_z >= 3)
```

```{r}
# calculate outlier-rate per id for rts and path

data_pp <- data_pp %>%
   group_by(id) %>%
   mutate(
     id_rt_outlier = ((sum(rt_ms_z < -3) + sum(rt_ms_z > 3)) / first(n_trials)) * 100,
     id_tracked_path_outlier = ((sum(tracked_path_z < -3) + sum(tracked_path_z > 3)) / first(n_trials)) * 100
     ) %>%
   ungroup()

# delete all rts and path > 3 SDs
n <- nrow(data_pp)

data_pp <- filter(data_pp, rt_ms_z >= -3 & rt_ms_z <= 3 & tracked_path_z >= -3 & tracked_path_z <= 3)

cat("Deleted: ", n - nrow(data_pp), " trials")
```


```{r}
# inspect rt data again
ggplot(data_pp,aes(id, rt_ms)) +
  geom_boxplot()
```

```{r}
# inspect path data again
ggplot(data_pp,aes(id, tracked_path)) +
  geom_boxplot()
```

```{r}
# inspect rt data distribution

ggplot(data_pp, aes(rt_ms)) +
  geom_histogram(bins = 100)
```

```{r}
# inspect path data distribution

ggplot(data_pp, aes(tracked_path)) +
  geom_histogram(bins = 100)
```

```{r}
## calculate rate of included trials per subject
data_pp <- data_pp %>%
  group_by(id) %>%
  mutate(
    trials_incl = n(),
    incl_trials_rate = (trials_incl / n_trials) * 100
  ) %>%
  ungroup()


### calculating mean rt and path (for Subject-outlier-detection)
data_pp <- data_pp %>%
  group_by(id) %>%
  mutate(
    vp_rt = mean(rt_ms),
    vp_path = mean(tracked_path),
    ) %>%
  ungroup()
```


## Aggregate data

```{r}
### Aggregate rt and path (real_weight x virtual_weight)
data_long <- data_pp %>%
  group_by(id, real_weight, virtual_weight) %>%
  summarise(
    incl_trials_rate = first(incl_trials_rate),
    vp_rt = first(vp_rt),
    vp_path = first(vp_path),
    rt_ms_mean = mean(rt_ms),
    path_mean = mean(tracked_path)
  ) %>%
  ungroup()

```

## Restructure data

```{r}

# create wide from long

data_wide <- pivot_wider(data_long,
  names_from = c(real_weight, virtual_weight),
  values_from = c(rt_ms_mean, path_mean),
  names_sep = "_"
)

```

## Identify Outlier-Subjects (more than 3 x IQR above or below group median)

```{r}
# create empty exclusion variables
data_wide <- data_wide %>%
  mutate(excl = 0,
         excl_note = "")


### Participant-Outlier-Function
vp_outlier <- function(df, x) {
  q1 <- quantile(x, .25)
  q3 <- quantile(x, .75)
  iqr <- IQR(x)
  ids_excl <- subset(df, x < (q1 - 3 * iqr) | x > (q3 + 3 * iqr), select = "id")
  return(ids_excl)
}


### vp_rt
ggplot(filter(data_wide,excl == 0)) +
  geom_boxplot(aes(y = vp_rt), coef = 3)


```

```{r}
vp_outlier(data_wide[data_wide$excl == 0, ], data_wide[data_wide$excl == 0, ]$vp_path)
```

```{r}
# code subjects as outliers
#data_wide <- data_wide %>%
#  mutate(excl = ifelse(id == ##, 1, excl),
#         excl_note = ifelse(id == ##, "vp_rt", excl_note),
#         ) 


### transfer exclusion-variable to data_long
data_long <- inner_join(data_long, 
                        subset(data_wide, select = c(id, excl, excl_note)), 
                        by = "id")

### transfer exclusion-variable to data_pp
data_pp <- inner_join(data_pp, 
                      subset(data_wide, select = c(id, excl, excl_note)), 
                      by = "id")


```

# Statistical Analyses

## Setup libraries and functions

```{r message=FALSE}
library(rstatix)
library(psych)
library(effectsize)
library(knitr)
library(psychReport)
library(MetBrewer)
library(viridis)
library(ggsci)
library(ggpubr)
```

```{r}
my_lineplot <- function(data, x, y, group, title, xlab, ylab, grouplab, xticklabs, groupticklabs) {
  lineplot <- ggline(
    data,
    x = x, 
    y = y, 
    color = group,
    linetype = group,
    shape = group,
    add = "mean_ci",
    ci = 0.95,
    #title = title,
    xlab = xlab,
    ylab = ylab,
    size = 1,
    position = position_dodge(width = 0.10), 
  ) + 
  theme(
    legend.position = "right", 
    legend.direction = "vertical",
    axis.title.y = element_text(margin = margin(r = 10)),
    text = element_text(size = 16)
  ) +
  labs(
    color=grouplab,
    linetype=grouplab,
    shape=grouplab
  ) +
  grids(linetype = "dashed") +
  scale_x_discrete(labels=xticklabs) + 
  scale_color_discrete(type=c("#EE442F", "#63ACBE"), labels=groupticklabs) +
  scale_shape_discrete(labels=groupticklabs) + 
  scale_linetype_discrete(labels=groupticklabs) 
  
    
  return(lineplot)
}

```


## Exclude participants

```{r}
data_long <- filter(data_long,excl == 0)
data_wide <- filter(data_wide,excl == 0)
data_pp <- filter(data_pp,excl == 0)
```

## Preprocessing descriptives and mean performance

```{r}

descriptives <- describe(data_wide)
kable(descriptives, digits = 2)
```

## Analyses of rt

### visualize rt

```{r}
lineplot <- my_lineplot(
  data = data_long,
  x = "real_weight", 
  y = "rt_ms_mean",
  group = "virtual_weight",
  title = "Movement Time per Real and Virtual Weight",
  xlab = "Controller",
  ylab = "Movement Time (Milliseconds)",
  grouplab = "Visual Representation",
  xticklabs = c("Heavy Control.", "Light Control."),
  groupticklabs = c("Heavy Model", "Light Model")
)

ggsave(filename = "rt_ms_figure.png", plot = lineplot)

lineplot
```


### Summarize data

```{r}


data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(rt_ms_mean, type = "full", show = c("n", "mean", "sd", "ci"))
```

### 2 x 2 repeated measures ANOVA

```{r}
rt_model <- data_long %>% 
  rstatix::anova_test(dv = rt_ms_mean,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 3,
                         effect.size = "pes")


kable(rt_model)
```

## Analyses of path

### visualize path

```{r}
lineplot <- my_lineplot(
  data = data_long,
  x = "real_weight", 
  y = "path_mean",
  group = "virtual_weight",
  title = "Movement Path per Real and Virtual Weight",
  xlab = "Controller",
  ylab = "Movement Path of Pointer (Meters)",
  grouplab = "Visual Representation",
  xticklabs = c("Heavy Control.", "Light Control."),
  groupticklabs = c("Heavy Model", "Light Model")
)

ggsave(filename = "path_figure.png", plot = lineplot)

lineplot
```

### Summarize data

```{r}
data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(path_mean, type = "full", show = c("n", "mean", "sd", "ci"))
```

### 2 x 2 repeated measures ANOVA

```{r}
path_model <- data_long %>% 
  rstatix::anova_test(dv = path_mean,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 3,
                         effect.size = "pes")

kable(path_model)
```
