---
title: "Questionnaires"
format: 
  html: 
    toc: true
    embed-resources: true
editor: visual
---

# Preprocessing

## Setup

```{r message=FALSE}

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

rm(list = setdiff(ls(),"data_raw"))
library(tidyverse)
library(knitr)

```

## Read raw data

```{r message=FALSE}
# read data

data_raw <- read_csv("../data/questionnaire_acc.csv")

head(data_raw)
```

## define factors

```{r}
data_pp <- data_raw


# factors
data_pp <- data_pp %>%
  mutate(
    id = factor(participant_id),
    real_weight = factor(real_weight),
    virtual_weight = factor(virtual_weight)
  )
```


## Aggregate data

```{r}
# calculae prjq factors
data_long <- data_pp %>%
  group_by(id, real_weight, virtual_weight) %>%
  summarise(
    borg = borg,
    prjq_fac_1 = sum(q2, q9, q11, q17, q18, q32, q37, q38),
    prjq_fac_2 = sum(q21, q36, q40, q54, q56, q60),
    prjq_fac_3 = sum(q30, q48, q61, q70),
  ) %>%
  ungroup()
```

## Restructure data

```{r}

# create wide from long

data_wide <- pivot_wider(data_long,
  names_from = c(real_weight, virtual_weight),
  values_from = c(borg, prjq_fac_1, prjq_fac_2, prjq_fac_3),
  names_sep = "_"
)
```


# Statistical Analyses

## Setup libraries and functions

```{r message=FALSE}
library(rstatix)
library(psych)
library(effectsize)
library(knitr)
library(psychReport)
library(MetBrewer)
library(viridis)
library(ggsci)
library(ggpubr)
```


## Preprocessing descriptives and mean performance

```{r}
descriptives <- describe(data_wide)
kable(descriptives, digits = 2)
```

## Analyses of PRJQ

### Visualize all Factors

```{r}
my_barplot <- function(data, x, y, title, group, xlab, ylab, grouplab, xticklabs, groupticklabs) {
  barplot <- ggbarplot(
      data,
      x = x,
      y = y,
      fill = group,
      add = "mean_se",
      ylab = ylab,
      title = title,
      #size = 1,
      position = position_dodge(width = 0.80), 
    ) + 
    theme(
      axis.title.x = element_blank(),
    ) +
    labs(
      fill=grouplab,
    ) +
    grids(linetype = "dashed") +
    scale_x_discrete(labels=xticklabs) + 
    scale_fill_discrete(type=c("#EE442F", "#63ACBE"), labels=groupticklabs) +
    scale_shape_discrete(labels=groupticklabs) + 
    scale_linetype_discrete(labels=groupticklabs) 
  return(barplot)
}

line_fac_1 <- my_barplot(data_long,
    x = "real_weight",
    y = "prjq_fac_1",
    group = "virtual_weight",
    title = "Factor 1",
    ylab = "Score",
    grouplab = "Displayed Controller",
    xticklabs = c("Heavy C.", "Light C."),
    groupticklabs = c("Heavy Model", "Light Model")
    )

line_fac_2 <- my_barplot(data_long,
    x = "real_weight",
    y = "prjq_fac_2",
    group = "virtual_weight",
    title = "Factor 2",
    ylab = "Score",
    grouplab = "Displayed Controller",
    xticklabs = c("Heavy C.", "Light C."),
    groupticklabs = c("Heavy Model", "Light Model")
    )

line_fac_3 <- my_barplot(data_long,
    x = "real_weight",
    y = "prjq_fac_3",
    group = "virtual_weight",
    title = "Factor 3",
    ylab = "Score",
    grouplab = "Displayed Controller",
    xticklabs = c("Heavy C.", "Light C."),
    groupticklabs = c("Heavy Model", "Light Model")
    )

title_plot <- text_grob("Results of PRJQ Factors 1 to 3", size = 16) %>% as_ggplot()

ggarrange(NULL, title_plot, NULL, line_fac_1, line_fac_2, line_fac_3, nrow = 2, ncol = 3, heights = c(1,3), legend = "bottom", common.legend = TRUE) +
  coord_fixed(ratio = 0.4)

```


### Summarize all Factors

#### PRJQ Factor 1

```{r}
data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(prjq_fac_1, type = "mean_sd")
```

#### PRJQ Factor 2

```{r}
data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(prjq_fac_2, type = "mean_sd")
```

#### PRJQ Factor 3

```{r}
data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(prjq_fac_3, type = "mean_sd")
```

### 2 x 2 repeated measures ANOVA

#### PRJQ Factor 1

```{r}
rt_model <- data_long %>% 
  rstatix::anova_test(dv = prjq_fac_1,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 2,
                         effect.size = "pes")

kable(rt_model)
```

#### PRJQ Factor 2

```{r}
rt_model <- data_long %>% 
  rstatix::anova_test(dv = prjq_fac_2,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 2,
                         effect.size = "pes")

kable(rt_model)

```

#### PRJQ Factor 3

```{r}
rt_model <- data_long %>% 
  rstatix::anova_test(dv = prjq_fac_3,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 2,
                         effect.size = "pes")

kable(rt_model)

```
## Analyses of BORG

### Visualize

```{r}
my_barplot(data_long,
    x = "real_weight",
    y = "borg",
    group = "virtual_weight",
    title = "Percieved exhaustion via BORG (better name needed)",
    ylab = "BORG Score",
    grouplab = "Displayed Controller",
    xticklabs = c("Heavy Controller", "Light Controller"),
    groupticklabs = c("Heavy Model", "Light Model")
    ) + 
  theme(
    legend.position = "right", 
    legend.direction = "vertical",
    axis.title.y = element_text(margin = margin(r = 10))
  ) +
  coord_cartesian(ylim = c(6, NA))
```

### Summarize

```{r}
data_long %>%
  group_by(real_weight, virtual_weight) %>%
  get_summary_stats(borg, type = "mean_sd")
```

### 2 x 2 repeated measures ANOVA

```{r}
rt_model <- data_long %>% 
  rstatix::anova_test(dv = borg,
                         wid = id,
                         within = c(real_weight, virtual_weight),
                         type = 2,
                         effect.size = "pes")

kable(rt_model)
```
